\ifgerman{\chapter*{Inhaltsangabe}}{\chapter*{Abstract}}

Graph database management systems have emerged as specialized databases that can store and process relationships among the data entities in an efficient way. Graph databases are equipped with many components that work together in order to handle even the very complex relationships that can exist in a network of connected data. One of the main components of a graph database is its storage system. The storage system of a graph database is utilizing a set of graph data structures in order to efficiently manage the storage of graph data. 

For the construction of a graph storage system; many graph data structures are available as alternatives to choose from. Each graph data structure has its unique way in representing graph data. The different representations of graph data implies a difference in the complexity of the data storage and retrieval operations performed on each of the graph data structures. Choosing the right graph data structure for the storage of graph data is challenging without a comprehensive bench-marking of the many available graph data structures.

In this thesis, we study the way each graph data structure is representing the graph data stored from logical and physical perspective. We evaluate the performance of the graph data structures according to a set of well-defined dimensions. Our evaluation of the graph data structures is based on an in-memory implementation of the data structures. 

By the end of this thesis, we will answer evaluation questions concerning the scalability, loading, and query performance of a set of graph data structures. We believe the answers to those questions will aid graph database designers in their choices for the graph data structure to use.

{\chapter*{Acknowledgements}}

It is a pleasure to finally get this work done. I would like to thank my advisors Prof. Gunter Saake, and M.Sc. Gabriel Campero Durand for their support, guidance, and supervision throughout my journey in writing this thesis. 

Also, I would like to thank my family and friends for the continuous support, and encouragement they have shown me during my entire master's studies, and especially during my thesis writing.





{\chapter*{Declaration of Academic Integrity}}

I hereby declare that this thesis is solely my own work and I have cited all external sources used.

\textit{Magdeburg, November 12th 2018} 



\begin{flushright}
\textbf{——————–} \\
\textbf{Sameh Manaa}
\end{flushright}
